\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework

### 2016-06-05 MovePattern_CAGIS/Twitter_MovementPatterns_VisualAnalytics.tex
revision

\begin{document}
%\input{./Title.tex}
%\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
	\author{}
%	\author[1, 2, 3]{Junjun Yin}
%	\author[1, 2, 3, 4]{Shaowen Wang}	
%%	\author[1, 2, 3, 4, \footnote{Corresponding author: shaowen@illinois.edu}]{Shaowen Wang}
%	
%	\affil[1]{
%	\it	CyberGIS Center for Advanced Digital and Spatial Studies
%	}
%	\affil[2]
%	{
%	\it	CyberInfrastructure and Geospatial Information Laboratory
%	}
%	\affil[3]
%	{
%	\it	Department of Geography and Geographic Information Science
%	}
%	\affil[4]
%	{
%	\it	National Center for Supercomputing Applications \authorcr
%	\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
%	}

@@

\pagenumbering{gobble}
\onehalfspacing
\section*{\begin{center}
Abstract
\end{center}}
Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
In this study, we have extracted high-resolution mobility data from a collection of 1.3 billion geo-located Twitter messages to study multi-scale spatiotemporal Twitter user mobility patterns in the United States during the year 2014. 
Regarding the concerns of infringement on individual privacy, such as the mobile phone call data with restricted access, the dataset is collected from publicly accessible Twitter data streams.
In this study, we have developed a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
We have performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal granularity.
In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed different groups of Twitter users with multi-scale or multi-modal mobility patterns.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
\newline

\noindent\textbf{Keywords:} Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework\\

Notes: What about randomly choose several states and perform the analysis
\cleardoublepage

@@

The remainder of this paper is organized as follows.
Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, geo-located Twitter data.
We focus on research challenges in visual-analytics methods to enable multi-scale
spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
In particular, we look into high performance distributed computing approach for addressing such challenges.
Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
Section 4 presents the case study of performing visual-analytics for seeking Twitter mobility patterns in the United States of year 2014. Section 5 concludes the paper.

@@

\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
Mobility data is essentially a collection of spatiotemporal records of people moving from one location to another in the geographic space.
To study mobility patterns of individuals, a space-time trajectory~\citep{hagerstrand1985time} of each individual should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\citep{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\citep{kwan2004geovisualization}. While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\citep{andrienko2007designing}.
For example, a visual clutter problem is likely to occur when visualizing massive amount of user trajectories, which makes it difficult for capture meaningful mobility patterns.

Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g. countries, states, and cities, etc.) and identify the changes over space and time~\citep{maceachren2001research, maceachren2004maps}.
In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\citep{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\citep{andrienko2007designing}.
Also, it is useful to group the subsets of user trajectories based on the shared characteristics for smooth transformations of space and time. For example, a network approach was used to summarize the actual movements in Twitter user trajectories as movement flows among different countries~\citep{hawelka2014geo}.

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at. In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it. 
In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: -167.276413, longitude: 5.499550) and upper right (latitude: -52.233040, longitude: 83.162102).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.

@@

\subsection{Twitter user population dynamics}
To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
For this study, we have derived the census information of 48 states plus Washington, D.C., and 3108 counties of the United States (i.e., excluding Alaska and Hawaii) of year 2014 from the US census bureau\footnote{http://www.census.gov/}.
For every state and county, the framework summarizes the number of unique users in each unit for the year 2014 (as well as every month). 
The results of the correlations between the number of unique Twitter user and the census population estimates in each state is show in Figure 3. 
\newline

\begin{figure}[h]
\centering
\includegraphics[width=1\linewidth]{./figures/test}
\caption{The correlation between the number of unique Twitter user and the census population estimates in each state (a) based on year 2014 and (b) based on each month of year 2014}
\label{fig:Arch}
\end{figure}
\FloatBarrier

The results show that the number of unique Twitter users is well ($R^{2}=0.92$ and p-value $<$ 0.01) correlated with the state level census population estimates in year 2014 (Figure 3(a)) and it is consistent (with all $R^{2} > 0.95$ and p-value $<$ 0.01) in each month (Figure 3(b)).
However, such correlations are not significant at the county level. 
Interestingly, zero Twitter population were found in  4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year, which means no geo-located tweets were captured from those areas. 
It is not clear whether people in those 4 counties do not send geo-located tweets at all or the tweets were lost due to 1 \% policy mentioned in~\citep{hawelka2014geo} as both cases are unlikely. Nevertheless, this does show the limitation of directly using Twitter population as proxies of real population. 
In addition,  the dramatic difference between the correlations at state level and the county level could be useful for other researchers when studying population dynamics at a specific spatial scale.

@@

%\subsection{The interactive 3D virtual globe web mapping interface}
%In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, our framework integrates a 3D virtual globe web mapping interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements. 
%The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
%We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers,  for aggregating movements in different level-of-details.
%The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc. as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\citep{liu2014cybergis}.
%In return, the map interface visualizes the corresponding movement flows on the virtual globe.
%
%An overview of the web mapping interface is shown in Figure 9. In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query. 
%When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions. If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the mapping interface will automatically provide the corresponding level-of-details on the fly.
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=0.8\linewidth]{./figures/vocation}
%\caption{An overview of the 3D interactive web mapping interface}
%\label{fig:Web_Interface}
%\end{figure}
%%\FloatBarrier

@@

\section{Conclusions and Discussions}
In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014. 
To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop.
It delivers scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.

With this framework, we have found some interesting Twitter user mobility patterns, both statically and visually.
We first examined the Twitter population by exploring the correlations between the number of unique users and the census population estimates at both state and county level (excluding Hawaii and Alaska). 
Although these two correlate well at the state level, there is no significance at the county level. 
Interestingly, no geo-located Twitter messages were found in 4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year.
We then studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which provides supports that we are not just capturing a random snapshot of the whole data stream.

We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function. In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.   
More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.
In particular, by comparing the mobility patterns revealed by displacements and radius of gyrations of Twitter users in the United States and Australia, there are slightly difference regarding the exact value of distance bounds between different fitting functions. 
However, the fact that these measurements are of people (i.e., Twitter users) in different countries (in this case, continent) and their probability distributions can all be approximated by a combination of three functions, has clearly show the values in using geo-located tweets for conducting replicable human mobility studies.

>>>>

\begin{document}
%\input{./Title.tex}
\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
%\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
	\author{}
%	\author[1, 2, 3]{Junjun Yin}	
%	\affil[1]{
%	\it	CyberGIS Center for Advanced Digital and Spatial Studies
%	}
%	\affil[2]
%	{
%	\it	CyberInfrastructure and Geospatial Information Laboratory
%	}
%	\affil[3]
%	{
%	\it	Department of Geography and Geographic Information Science\authorcr
%		\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
%	}

@@

\pagenumbering{gobble}
\onehalfspacing
\section*{\begin{center}
Abstract
\end{center}}
Understanding human mobility patterns is of great importance for urban planning, traffic management, and even marketing campaign.
However, the capability of capturing detailed human movements with fine-grained spatial and temporal granularity is still limited.
In this study, we have extracted high-resolution mobility data from a collection of 1.3 billion geo-located Twitter messages to study multi-scale spatiotemporal Twitter user mobility patterns in the United States during the year 2014. 
Regarding the concerns of infringement on individual privacy, such as the mobile phone call data with restricted access, the dataset is collected from publicly accessible Twitter data streams.
In this study, we have developed a scalable visual-analytics framework to deliver efficiency and scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-scale spatiotemporal user mobility patterns.
We have performed a set of statistical analysis to understand Twitter user mobility patterns across multi-level spatial scales and temporal granularity.
In particular, the Twitter user mobility patterns measured by the displacements and radius of gyrations of individuals have revealed multi-scale or multi-modal Twitter user mobility patterns.
By further studying such mobility patterns in different temporal ranges, we have identified both consistency and seasonal fluctuations regarding the distance decay effects in the corresponding mobility patterns.
\newline

\noindent\textbf{Keywords:} Geo-located tweets, mobility patterns, multi-scale spatiotemporal analysis, scalable visual-analytics framework\\
\cleardoublepage

@@

The remainder of this paper is organized as follows.
Section 2 describes the related work in the context of studying mobility patterns using LBSM data, in particular, geo-located Twitter data.
We focus on research challenges in visual-analytics methods to enable multi-scale
spatiotemporal analysis with massive movement datasets, including data management, multi-level spatiotemporal user trajectory modeling and visualization.
Section 3 details the processes for extracting, aggregating and summarizing multi-level spatiotemporal Twitter user mobility patterns.
Section 4 presents the case study of performing visual-analytics for seeking Twitter mobility patterns in the United States of year 2014. Section 5 concludes the paper.

@@

\subsection{Data-intensive challenges for multi-scale geo-visual analytics}
Mobility data is essentially a collection of spatiotemporal records of people moving from one location to another in the geographic space.
To study mobility patterns of individuals, a space-time trajectory~\citep{hagerstrand1985time} of each individual should be modeled and constructed to quantify the collective movements over space and time.
Based on the extracted space-time trajectories, aforementioned studies are able to perform analysis, such as the measurements of displacements and radius of gyrations of individuals, to study the mobility dynamics.
At the same time, space-time trajectory is one of the core concepts in H{\"a}gerstrand's time geography to understand the embedded spatiotemporal dynamics~\citep{hagerstrand1985time}, which has provided useful insights to explore movements across different geographical scales and temporal granularity.
For example, a geo-visualization approach was used to study human activity patterns, where user trajectories are mapped in a 3D space ordered by timestamps in the third dimension~\citep{kwan2004geovisualization}. While such an approach enables visualization of detailed trajectories, its capability is limited in dealing with large-volume movement datasets~\citep{andrienko2007designing}.
Instead of directly visualizing individual user trajectories, a space-time cube approach was proposed in analyzing and visualizing the collective trajectories by providing flexibilities in setting up both spatial and temporal ranges, and therefore to study the mobility patterns across different spatial units (e.g. countries, states, and cities, etc.) and identify the changes over space and time~\citep{maceachren2001research, maceachren2004maps}.
In this connection, visual-analytics methods are proposed to help better convey the findings in terms of analyzing and visualizing multi-level spatiotemporal mobility patterns~\citep{andrienko2007designing,andrienko2007visual}.
Visual-analytics methods focus on the synergy of computational and analytical methods to reduce the visual clutter, where aggregation methods are suggested to perform grouping/dividing individual's moving trajectories at different spatial and temporal granularity, e.g., utilizing the space-time cube approach~\citep{andrienko2007designing}.

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at. In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it. 
In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.

@@

%\subsection{An overview of the Twitter user population}
%To investigate the overall geographical distribution of the Twitter population in our dataset, we have carried out analysis at both county and state level to test their correlations and stability regarding the census population estimates.
%For this study, we have derived the census information of 48 states plus Washington, D.C., and 3108 counties of the United States (i.e., excluding Alaska and Hawaii) of year 2014 from the US census bureau\footnote{http://www.census.gov/}.
%For every state and county, the framework summarizes the number of unique users in each unit for the year 2014 (as well as every month). 
%The results of the correlations between the number of unique Twitter user and the census population estimates in each state is show in Figure 3. 
%\newline
%
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=1\linewidth]{./figures/test}
%\caption{The correlation between the number of unique Twitter user and the census population estimates in each state (a) based on year 2014 and (b) based on each month of year 2014}
%\label{fig:Arch}
%\end{figure}
%\FloatBarrier
%
%The results show that the number of unique Twitter users is well ($R^{2}=0.92$ and p-value $<$ 0.01) correlated with the state level census population estimates in year 2014 (Figure 3(a)) and it is consistent (with all $R^{2} > 0.95$ and p-value $<$ 0.01) in each month (Figure 3(b)).
%However, such correlations are not significant at the county level. 
%Interestingly, zero Twitter population were found in  4 (out of 3108) counties (i.e., Manassas Park city, Covington city, Cumberland county, Lipscomb county) throughout the year, which means no geo-located tweets were captured from those areas. 
%It is not clear whether people in those 4 counties do not send geo-located tweets at all or the tweets were lost due to 1 \% policy mentioned in~\citep{hawelka2014geo} as both cases are unlikely. Nevertheless, this does show the limitation of directly using Twitter population as proxies of real population. 
%In addition,  the dramatic difference between the correlations at state level and the county level could be useful for other researchers when studying population dynamics at a specific spatial scale.

@@

\subsection{The interactive 3D virtual globe web mapping interface}
In addition to providing supports for understanding Twitter user mobility patterns with statistical analysis, the framework integrates a 3D virtual globe interface to enable users to perform exploratory geo-visual analytics of the multi-level spatiotemporal Twitter user movements. 
The 3D virtual globe is developed and extended from the Cesium library\footnote{http://cesiumjs.org/}, which is an open-source WebGL virtual globe and map engine. 
We customized the map engine to adapt different spatial scales, which correspond to the hierarchical spatial layers,  for aggregating movements in different level-of-details.
The map interface interprets user's interactions, such as area-of-interest, time window, and zoom levels, etc. as parameters and send to the dedicated visualization servlet on the CyberGIS Gateway\footnote{http://sandbox.cigi.illinois.edu/home/}, which is the leading online cyberGIS environment for a large number of users to perform computing- and data-intensive, and collaborative geospatial problem-solving enabled by advanced cyberinfrastructure~\citep{liu2014cybergis}.
In return, the map interface visualizes the corresponding movement flows on the virtual globe.

An overview of the web mapping interface is shown in Figure 9. In terms of performing exploratory visual-analytics of Twitter user movement patterns, users can specify the time window to enable the query. 
When the results are shown, users can hover the mouse over each individual lines on the map to see the value of movement flows for both in and out directions. If the selected criteria keep unchanged, whenever the user zooms in/out, tilt or rotate the globe, the mapping interface will automatically provide the corresponding level-of-details on the fly.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{./figures/vocation}
\caption{An overview of the 3D interactive web mapping interface}
\label{fig:Web_Interface}
\end{figure}
%\FloatBarrier

@@

\section{Conclusions}
In this study, we have used large volume of geo-located tweets to study Twitter user mobility patterns across multi-level spatial scales and temporal granularity in the United States during the year 2014. 
To address the data-intensive challenges, we have developed a scalable visual-analytics framework tailored to accommodate large volume of geo-located tweets for studying multi-level spatiotemporal Twitter user mobility patterns.
This framework is implemented based on high-performance distributed computing environment using Apache Hadoop.
It delivers scalability in filtering large volume of geo-located tweets, modeling and extracting Twitter user movements, generating space-time user trajectories, and summarizing multi-level spatiotemporal user mobility patterns.

With this framework, we have found some interesting Twitter user mobility patterns, both statically and visually.
We studied the collective Twitter user visiting behavior regarding the frequency of Twitter users visiting different locations, which was fitted by a two-tier power-law distribution function.
The two-tier power law distribution indicates that the collective behaviors of Twitter user visiting different locations can be well approximated with a (truncated) L\'{e}vy Walk model, which has also been identified in many human mobility studies using different mobility data.
The similarities among the cumulative distributions suggest that the mobility data collected from geo-located tweets are temporally stable, at least at the monthly interval, which provides supports that we are not just capturing a random snapshot of the whole data stream.

We studied the distance decay effects in the collective Twitter user movements measured by the probability distributions of the displacements and radius of gyrations of individuals. 
These distributions can all be approximated by a combination of three functions: an exponential function, a stretched-exponential function and a power-law function. In particular, distance bounds between different fitting functions in displacement distribution reveals the existence of multi-scale or multi-modal mobility patterns of the Twitter users in the United States, whereas the distribution of radius of gyration reveals different groups of Tweet users with different types of spatial coverages.   
More importantly, we further studied these mobility patterns in different temporal scales to investigate the temporal changes in the mobility patterns. 
We found that the accumulated displacements are almost identical in different months, while the long distance radius of gyration (i.e., above 30 km) will experience more seasonal changes in the Twitter user mobility pattern.

### 2016-06-05 backups/MovePattern_revision/Twitter_MovementPatterns_VisualAnalytics.tex
revision

\begin{document}
%\input{./Title.tex}
\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
%\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
	\author{}
%	\author[1, 2, 3]{Junjun Yin}	
%	\affil[1]{
%	\it	CyberGIS Center for Advanced Digital and Spatial Studies
%	}
%	\affil[2]
%	{
%	\it	CyberInfrastructure and Geospatial Information Laboratory
%	}
%	\affil[3]
%	{
%	\it	Department of Geography and Geographic Information Science\authorcr
%		\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
%	}

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at. In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it. 
In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: 5.4, longitude: -167.3) and upper right (latitude: 83.2, longitude: -52.2).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.

>>>>

\begin{document}
%\input{./Title.tex}
\title{\itshape Exploring multi-scale spatiotemporal Twitter user mobility patterns with a scalable visual-analytics framework}
%\title{\itshape Exploring Multi-scale Spatiotemporal Twitter User Mobility Patterns Using Geo-located Twitter Data}
	\author{}
%	\author[1, 2, 3]{Junjun Yin}
%	\author[1, 2, 3, 4]{Shaowen Wang}	
%%	\author[1, 2, 3, 4, \footnote{Corresponding author: shaowen@illinois.edu}]{Shaowen Wang}
%	
%	\affil[1]{
%	\it	CyberGIS Center for Advanced Digital and Spatial Studies
%	}
%	\affil[2]
%	{
%	\it	CyberInfrastructure and Geospatial Information Laboratory
%	}
%	\affil[3]
%	{
%	\it	Department of Geography and Geographic Information Science
%	}
%	\affil[4]
%	{
%	\it	National Center for Supercomputing Applications \authorcr
%	\it	University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA
%	}

@@

\section{Materials and Methods}
\subsection{Geo-located Twitter data}
Geo-located tweets are tweets appended with an additional geo-tag in the form of a pair of geographical coordinates, which represents the location a tweet was sent at. In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it. 
In our case, to ensure the complete coverage over the United States, we implemented a crawler that selects North America as the initial area-of-interest, where the geographical boundary is specified with lower left (latitude: -167.276413, longitude: 5.499550) and upper right (latitude: -52.233040, longitude: 83.162102).
The crawler is constantly running with over 2 million geo-located raw tweets ($\sim$2GB in size) collected per day.
We have collected more than 1.3 billion geo-located tweets from 1$^{st}$ January to 31$^{st}$ December, 2014 with 6,147,430 Twitter users and 1 TB in file size.
